\textls[-0]{\thetitle}

### 2023-03-22 casestudies.tex
Update qualitative statistic for analysis case.

@@

>>>>

% I think the following is a bit weird ... not enough quantative and not enough qualititive
% When programming in a direct style, before using \Lang, the STLC base module 
% will take around 350LOCs, and STLC with one feature is around 400 LOCs, because
% it requires to repeat the definition of the STLC base definition. It will take 
% more space when we add more features into STLC.

% After using \Lang, the 
% STLC base family also take about 350 LOCs. However, one feature as children family takes only about 100~250 LOCs. What's more, the mixin of two features usually only take 1~20 LOCs.
When programming in a direct style, before using \Lang, the STLC base module will take around 350 LOCs while using \Lang, the STLC base family takes about same amount of the code.

However, without \Lang, STLC with one feature will require around 400 LOCs as the definition of STLC base is repeated. On the other hand, using \Lang, each feature as extended family only requires ranging from 100~250 LOCs. What's more, without \Lang, STLC with multiple features will require more and more while using \Lang's mixin feature, tens of LOCs is enough.

@@

If not using \Lang, we can construct \lsti{Imp}, \lsti{ImpGAI} and \lsti{ImpTI} in a similar way---but \lsti{Imp} is now a module instead of a family, \lsti{ImpGAI} is now a functor instead of a family with overridable fields, and \lsti{ImpTI} is a concrete instantiation of the functor \lsti{ImpGAI}. However, \lsti{ImpCP} cannot reuse the above framework as it extends syntax with natural numbers. Thus \lsti{ImpCP} will require repeating a large amount of definitions, and it alone will needs about 900~LOCs.
